### 2023-10-09 main.tex
Update main.tex
app

We introduce the Hamiltonian operator
\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian that describes the interaction between two connected sites is
\begin{equation}\label{edgeHamiltonian}
\mathcal{H}_{x,y}=\sum_{a,b=1}^{N}\Big(E_{ab}^{x} E_{b a}^{y}-E_{bb}^{x} E_{aa}^{y}\Big)
 \end{equation}
  and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)
\end{equation}
Here $E_{ab}^{x}$ is a copy of $E_{ab}$ defined in \eqref{actionE} acting on site $x$ (and
acting trivially as the identity on the other sites). 
Following  \cite{belitsky2015self}, the Hamiltonian and the Markov generator are linked by
\begin{equation}\label{Hamiltonian-Generator}
H=\mathcal{L}^{T}\dt
\end{equation}
The action of the generator can also be expressed as 
\begin{equation}
    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
\end{equation}
where 
\begin{equation}
    \langle f|=\sum_{ {{\bf m}\in \Omega}}f( {\bf m})\langle  {\bf m}|
\end{equation}

@@

\subsection{Integrable process on a line segment}\label{subsection-description-process-LINE}
In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$. These reservoirs, exchanging particle with the external environment, put the chain out of equilibrium. The Hamiltonian that we consider here is obtained from \eqref{OriginalHamiltonian} assuming that the conductances are
\begin{equation}
	\omega_{x,y}=\begin{cases}
		1 \quad \text{if}\quad |x-y|=1\\
		0\quad \text{otherwise}
	\end{cases}
\end{equation}
and the coupling to reservoirs are
\begin{equation}
	\Gamma_{x}=\begin{cases}
		1\quad \text{if} \quad x\in \{1,L\}\\
		0\quad \text{otherwise}
	\end{cases}
\end{equation}
We further assume that the maximal occupancy in each site is $\nu=1$, i.e. that there is an \textit{hard-core interaction}.
We will denote the element of the representation of the $gl(N)$  Lie algebra with $\nu=1$ by lowercase letters, i.e. $(e_{ab})_{a,b\in\{1,\ldots,N\}}$, to highlight that we are in the first fundamental representation of the algebra.
The Hamiltonian now reads
\begin{equation}\label{hamiltonian}
	H=H_{left}+H_{bulk}+H_{right}
\end{equation}
where
\begin{equation}
	H_{bulk}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
\end{equation}
Here $\mathcal{H}_{x,x+1}$  is a copy (acting on the vertices of the edge $x,x+1$) of the two-site Hamiltonian
\begin{equation}\label{H-corsivo}
	\begin{split}
		\mathcal{H}=P-\id
	\end{split}
\end{equation}
with 
\begin{equation}
	P=\sum_{a,b=1}^Ne_{ab}\otimes e_{ba}.
\end{equation} 
The action of $\mathcal{H}$ amounts to the permutation of the occupations of the two sites, i.e.
\begin{equation}
	\begin{split}
		\mathcal{H}|n\rangle\otimes   |m\rangle&=|m\rangle \otimes |n\rangle-|n\rangle \otimes|m\rangle\dt
	\end{split}
\end{equation}
The boundary terms are given by 
\begin{equation}
	H_{left}=\begin{pmatrix}
		\alpha_{1}-1&\alpha_{1}&\alpha_{1}&\ldots&\ldots&\alpha_{1}\\
		\alpha_{2}&\alpha_{2}-1&\alpha_{2}&\ldots&\ldots&\alpha_{2}\\
		\vdots&\vdots& &\ddots& &\vdots\\
		\alpha_{N-1}&\alpha_{N-1}&\ldots&\ldots&\alpha_{N-1}-1&\alpha_{N-1}\\
		\alpha_{N}&\alpha_{N}&\ldots&\ldots&\alpha_{N}&\alpha_{N}-1
	\end{pmatrix}
\end{equation}
\begin{equation}
	H_{right}=\begin{pmatrix}
		\beta_{1}-1&\beta_{1}&\beta_{1}&\ldots&\ldots&\beta_{1}\\
		\beta_{2}&\beta_{2}-1&\beta_{2}&\ldots&\ldots&\beta_{2}\\
		\vdots&\vdots& &\ddots& &\vdots\\
		\beta_{N-1}&\beta_{N-1}&\ldots&\ldots&\beta_{N-1}-1&\beta_{N-1}\\
		\beta_{N}&\beta_{N}&\ldots&\ldots&\beta_{N}&\beta_{N}-1
	\end{pmatrix}
\end{equation}
where, without loss of generality,  we assume that the parameters satisfy
\begin{equation}\label{ratesConditions}
	\sum_{a=1}^{N}\alpha_{a}=1,\qquad\sum_{a=1}^{N}\beta_{a}=1
\end{equation} 
We define also 
\begin{equation}\label{lambdaConditions}
	\lambda_{a}=\alpha_{a}-\beta_{a}\quad\text{with}\quad \sum_{a=1}^{N}\lambda_{a}=0\,.
\end{equation}
Under these assumption the Hamiltonian \ref{hamiltonian} is integrable (see \cite{vanicat2017exact} for its derivation within the Quantum Inverse Scattering method).

@@

The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
\begin{equation}\label{steadyStateH}
	|\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
\end{equation}
where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$
\begin{equation}
	\begin{split}
		\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
		\\&+
		\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right) 
		\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
		\\&
		\sum_{c_{1}=0}^{1-\delta_{\eta_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\eta_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}}^{(1-c_{y})(1-\delta_{\eta_{y},N})}
	\end{split}
\end{equation}
where we have introduced, $\forall x\in \{1,\ldots,L\}$
\begin{equation}
	\eta_{x}(b)=\begin{cases}
		\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
		d_{x}\qquad &\text{otherwise}
	\end{cases}%\qquad \theta_{x}=\begin{cases}
		%\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
		%	1 \qquad &\text{otherwise}
		%\end{cases}
	\end{equation}
	The dependence of $\eta_{x}(b)$ with respect to $b$ is usually understood for the sake of notation. 
\begin{comment}
	{\color{blue}
		\begin{equation}\label{steadyStateH-coeff}
			\begin{split}
				\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
				\\&+
				\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{s=1}^{b}\delta_{s_{q_{r}},N}\right) 
				\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
				\\&
				\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
				\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
				\\ &
				\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
				\prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
			\end{split}
		\end{equation}
	}
\end{comment}
\newline \newline
	\textbf{Remark}: we observe that if no holes are present, i.e. if $\tau_{x}\neq N$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
	\begin{equation}\label{LinkABS-corr}
		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
	\end{equation}
	When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.

	\paragraph{Proof of formula \eqref{steadyStateH}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$. Here is more convenient to consider the matrix $\mathcal{S}_{1}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain. This matrix $\mathcal{S}_{1}$ is given by
	\begin{equation}\label{S1-L1}
		\mathcal{S}_{1}^{-1}=\sum_{\tau_{1}=1}^{N}e_{\tau_{1}}^{\tau_{1}}+(-1)\delta_{\tau_{1},N}\sum_{d_{1}=1}^{N-1}e_{1}^{d_{1}}
	\end{equation}
	Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
	\begin{equation}
		\begin{split}
			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
			\\&
			+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\} 
		\end{split}
	\end{equation}
	where we have introduced, $\forall x\in \{1,\ldots,L\}$
	\begin{equation}
		%\eta_{x}=\begin{cases}
			%	\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
			%	d_{x}\qquad &\text{otherwise}
			%\end{cases}\qquad
			\theta_{x}(b)=\begin{cases}
				\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
				N \qquad &\text{otherwise}
			\end{cases}
		\end{equation}
		The dependence of $\theta(b)$ with respect to $b$ is usually understood for the sake of notation. 
		This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
		\begin{align*}
			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{1}^{-1}&=
			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right. \\&+\left. \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
			\\&\otimes
			\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},N}\sum_{d_{L+1}=1}^{N-1}e_{1}^{d_{L+1}}\right\}
			\\&=
			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}\right. \\&+\left. \sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{b}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
		\end{align*}
		\begin{comment}

@@

				\Psi(\bm{\tau}) &=\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}_{\bm{\tau}}|\Psi{'}\rangle=\Psi{'}(\tau_{1},\ldots,\tau_{L})+ 

@@

				+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}\Psi{'}(\eta_{1},\ldots,\eta_{L})

>>>>

We introduce the Hamiltonian operator
\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian that describes the interaction between two connected sites is
\begin{equation}\label{edgeHamiltonian}
\mathcal{H}_{x,y}=\sum_{a,b=1}^{N}\Big(E_{ab}^{x} E_{b a}^{y}-E_{bb}^{x} E_{aa}^{y}\Big)
 \end{equation}
  and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)
\end{equation}
Here $E_{ab}^{x}$ is a copy of $E_{ab}$ defined in \eqref{actionE} acting on site $x$ (and
acting trivially as the identity on the other sites). 
Following  \cite{belitsky2015self}, the Hamiltonian and the Markov generator are linked by
\begin{equation}\label{Hamiltonian-Generator}
H=\mathcal{L}^{T}\dt
\end{equation}
The action of the generator can also be expressed as 
\begin{equation}
    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
\end{equation}
where 
\begin{equation}
    \langle f|=\sum_{ {{\bf m}\in \Omega}}f( {\bf m})\langle  {\bf m}|
\end{equation}

@@

\subsection{Integrable process on a line segment}\label{subsection-description-process-LINE}
In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$. These reservoirs, exchanging particle with the external environment, put the chain out of equilibrium. The Hamiltonian that we consider here is obtained from \eqref{OriginalHamiltonian} assuming that the conductances are
\begin{equation}
	\omega_{x,y}=\begin{cases}
		1 \quad \text{if}\quad |x-y|=1\\
		0\quad \text{otherwise}
	\end{cases}
\end{equation}
and the coupling to reservoirs are
\begin{equation}
	\Gamma_{x}=\begin{cases}
		1\quad \text{if} \quad x\in \{1,L\}\\
		0\quad \text{otherwise}
	\end{cases}
\end{equation}
We further assume that the maximal occupancy in each site is $\nu=1$, i.e. that there is an \textit{hard-core interaction}.
We will denote the element of the representation of the $gl(N)$  Lie algebra with $\nu=1$ by lowercase letters, i.e. $(e_{ab})_{a,b\in\{1,\ldots,N\}}$, to highlight that we are in the first fundamental representation of the algebra.
The Hamiltonian now reads
\begin{equation}\label{hamiltonian}
	H=H_{left}+H_{bulk}+H_{right}
\end{equation}
where
\begin{equation}
	H_{bulk}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
\end{equation}
Here $\mathcal{H}_{x,x+1}$  is a copy (acting on the vertices of the edge $x,x+1$) of the two-site Hamiltonian
\begin{equation}\label{H-corsivo}
	\begin{split}
		\mathcal{H}=P-\id
	\end{split}
\end{equation}
with 
\begin{equation}
	P=\sum_{a,b=1}^Ne_{ab}\otimes e_{ba}.
\end{equation} 
The action of $\mathcal{H}$ amounts to the permutation of the occupations of the two sites, i.e.
\begin{equation}
	\begin{split}
		\mathcal{H}|n\rangle\otimes   |m\rangle&=|m\rangle \otimes |n\rangle-|n\rangle \otimes|m\rangle\dt
	\end{split}
\end{equation}
The boundary terms are given by 
\begin{equation}
	H_{left}=\begin{pmatrix}
		\alpha_{1}-1&\alpha_{1}&\alpha_{1}&\ldots&\ldots&\alpha_{1}\\
		\alpha_{2}&\alpha_{2}-1&\alpha_{2}&\ldots&\ldots&\alpha_{2}\\
		\vdots&\vdots& &\ddots& &\vdots\\
		\alpha_{N-1}&\alpha_{N-1}&\ldots&\ldots&\alpha_{N-1}-1&\alpha_{N-1}\\
		\alpha_{N}&\alpha_{N}&\ldots&\ldots&\alpha_{N}&\alpha_{N}-1
	\end{pmatrix}
\end{equation}
\begin{equation}
	H_{right}=\begin{pmatrix}
		\beta_{1}-1&\beta_{1}&\beta_{1}&\ldots&\ldots&\beta_{1}\\
		\beta_{2}&\beta_{2}-1&\beta_{2}&\ldots&\ldots&\beta_{2}\\
		\vdots&\vdots& &\ddots& &\vdots\\
		\beta_{N-1}&\beta_{N-1}&\ldots&\ldots&\beta_{N-1}-1&\beta_{N-1}\\
		\beta_{N}&\beta_{N}&\ldots&\ldots&\beta_{N}&\beta_{N}-1
	\end{pmatrix}
\end{equation}
where, without loss of generality,  we assume that the parameters satisfy
\begin{equation}\label{ratesConditions}
	\sum_{a=1}^{N}\alpha_{a}=1,\qquad\sum_{a=1}^{N}\beta_{a}=1\;.
\end{equation} 
We define also 
\begin{equation}\label{lambdaConditions}
	\lambda_{a}=\alpha_{a}-\beta_{a}\quad\text{with}\quad \sum_{a=1}^{N}\lambda_{a}=0\,.
\end{equation}
Under these assumption the Hamiltonian \ref{hamiltonian} is integrable (see \cite{vanicat2017exact} for its derivation within the Quantum Inverse Scattering method).

@@

The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
\begin{equation}\label{steadyStateH}
	|\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
\end{equation}
where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$
\begin{equation}
	\begin{split}
		\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
		\\&+
		\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right) 
		\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}
		\\&
		\sum_{c_{1}=0}^{1-\delta_{\eta_{1}^{b},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\eta_{L}^{b},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\eta_{y}^{b}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\eta_{y}^{b}}^{(1-c_{y})(1-\delta_{\eta_{y},N})}
	\end{split}
\end{equation}
where we have introduced, $\forall x\in \{1,\ldots,L\}$
\begin{equation}\label{eta-notation}
	\eta_{x}^{b}(q_{1},\ldots,q_{b})=\begin{cases}
		\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
		i_{q_{k}}\qquad &\text{if}\quad x=q_{k}\quad \text{with}\quad q_{k}\in\{q_{1},\ldots,q_{b}\}
	\end{cases}%\qquad \theta_{x}=\begin{cases}
		%\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
		%	1 \qquad &\text{otherwise}
		%\end{cases}
	\end{equation}
	The dependence of $\eta_{x}^{b}$ with respect to $(q_{1},\ldots,q_{b})$ is usually understood for the sake of notation. 
\begin{comment}
	{\color{blue}
		\begin{equation}\label{steadyStateH-coeff}
			\begin{split}
				\Psi(\bm{\tau})&=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
				\\&+
				\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{s=1}^{b}\delta_{s_{q_{r}},N}\right) 
				\sum_{d_{q_{1}}=2}^{N}\ldots\sum_{d_{q_{b}}=2}^{N}
				\\&
				\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{\tau_{x},N}}\sum_{c_{q_{1}}=1}^{1}\ldots\sum_{c_{q_{b}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
				\prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{\tau_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
				\\ &
				\beta_{\tau_{y}}^{(1-c_{y})(1-\delta_{\tau_{y},N})}
				\prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
			\end{split}
		\end{equation}
	}
\end{comment}
\newline \newline
	\textbf{Remark}: we observe that if no holes are present, i.e. if $\tau_{x}\neq N$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
	\begin{equation}\label{LinkABS-corr}
		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
	\end{equation}
	When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.

	\paragraph{Proof of formula \eqref{steadyStateH}} As a consequence of \eqref{S1-Inverse}, we only need to show how the transformation $S_{1}^{-1}$ acts on the vector $|\Psi^{'}\rangle$. Here is more convenient to consider the matrix $\mathcal{S}_{1}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and make explicitly the tensor product over the chain. This matrix $\mathcal{S}_{1}$ is given by
	\begin{equation}\label{S1-L1}
		\mathcal{S}_{1}^{-1}=\mathbbm{1}+(-1)\sum_{a=1}^{N-1}e_{Na}
	\end{equation}
thus
\begin{equation}
\mathcal{S}_{1}^{-1}|\mu\rangle=|\mu\rangle+(-1)\delta_{\mu<N}|N\rangle
\end{equation}
By taking the tensor product over the chain we obtain 
\begin{equation}
	\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\bm{\mu}\rangle=\left(|\mu_{1}\rangle+(-1)\delta_{\mu_{1}<N}|N\rangle\right)\otimes \ldots \otimes \left(|\mu_{L}\rangle+(-1)\delta_{\mu_{L}<N}|N\rangle\right)
\end{equation}
therefore, projecting on $\langle \bm{\tau}|$ we have
\begin{equation}
	\langle \bm{\tau}|	\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\bm{\mu}\rangle=\prod_{x=1}^{L}\left(\delta_{\mu_{x},\tau_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\mu_{x},i_{x}}\right)
\end{equation}
\begin{comment}
	Using the notation introduced in \eqref{notation1} and \eqref{notation2} we have that 
	\begin{equation}
		\begin{split}
			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}&=\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right.
			\\&
			+\left.\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\eta_{1},\ldots,\eta_{L}}^{\theta_{1},\ldots,\theta_{L}}\right\} 
		\end{split}
	\end{equation}
	where we have introduced, $\forall x\in \{1,\ldots,L\}$
	\begin{equation}
		%\eta_{x}=\begin{cases}
			%	\tau_{x}\qquad &\text{if}\quad x\neq 1,\ldots,b\\
			%	d_{x}\qquad &\text{otherwise}
			%\end{cases}\qquad
			\theta_{x}(b)=\begin{cases}
				\tau_{x}\qquad &\text{if}\quad x\notin \{q_{1},\ldots,q_{b}\}\\
				N \qquad &\text{otherwise}
			\end{cases}
		\end{equation}
		The dependence of $\theta(b)$ with respect to $b$ is usually understood for the sake of notation. 
		This is proved by induction. Indeed, for $L=1$ it is trivially true, by \eqref{S1-L1}. We assume that it is true for arbitrary $L\in \mathbb{N}$ and we prove that it holds for $L+1$. 
		\begin{align*}
			\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}\otimes \mathcal{S}_{1}^{-1}&=
			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}\right. \\&+\left. \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{r}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L}}^{\eta_{1},\ldots,\eta_{L}}\right\}
			\\&\otimes
			\left\{ \sum_{\tau_{1}=1}^{N}e_{\tau_{L+1}}^{\tau_{L+1}}+(-1)\delta_{\tau_{L+1},N}\sum_{d_{L+1}=1}^{N-1}e_{1}^{d_{L+1}}\right\}
			\\&=
			\sum_{\tau_{1}=1}^{N}\ldots\sum_{\tau_{L+1}=1}^{N}\left\{e_{\tau_{1},\ldots,\tau_{L+1}}^{\tau_{1},\ldots,\tau_{L+1}}\right. \\&+\left. \sum_{b=1}^{L+1}(-1)^{b}\sum_{q_{1}=1}^{L+1}\sum_{q_{2}=q_{1}+1}^{L+1}\ldots\sum_{q_{b}=q_{b-1}+1}^{L+1}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},N}\right)\sum_{d_{q_{1}}=1}^{N-1}\ldots\sum_{d_{q_{b}}=1}^{N-1}e_{\theta_{1},\ldots,\theta_{L+1}}^{\eta_{1},\ldots,\eta_{L+1}}\right\}
		\end{align*}
		\begin{comment}

@@

	By introducing the notation \eqref{eta-notation} and by considering 
		|\Psi^{'}\rangle=\sum_{\mu_{1},\ldots,\mu_{L}=1}^{N}\Psi^{'}(\bm{\mu})|\bm{\mu}\rangle
	\end{equation} we obtain  
				\Psi(\bm{\tau}) &=\langle\bm{\tau}|\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi{'}\rangle=\Psi{'}(\tau_{1},\ldots,\tau_{L})+ 

@@

				+\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{\tau_{q_{r}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{r}}=1}^{N-1}\Psi{'}(\eta_{1},\ldots,\eta_{L})
